\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2022-02-19 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_Rev1.tex
polishing rebuttal round 1

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\linewidth]{IEEE14marginalsCase0.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs of the generator $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup \textbf{Case I} described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values. The $\theta_i$ are in rad, the $\omega_i$ are in rad/s.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginalsCase0}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\linewidth]{IEEE14marginalsCase1.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs of the generator $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup \textbf{Case II} described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values. The $\theta_i$ are in rad, the $\omega_i$ are in rad/s.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginalsCase1}
\end{figure*}

@@

Fig. \ref{fig:IEEE14omegamarginalsCase12} shows the corresponding univariate $\omega_{i}$-marginal PDFs. In particular, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) helps compare the $\omega_{4}$ marginal evolution for bus 6 in the nominal (\textbf{Case I}) and post-fault (\textbf{Case II}) scenarios. Since \textbf{Case II} considers the failure of line 13, from Fig. \ref{fig:Motivating} we intuitively expect that the transient effects of this fault will be prominent for bus 6 (generator 4). Indeed, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) shows that although the $\omega_{4}$ marginals in both \textbf{Case I} and \textbf{II}, at all times have highest probability around $0$ rad/s, the post-fault marginals show larger spread or dispersion of the probability mass, as expected. That the generator 4 states in \textbf{Case II} have larger uncertainties than in \textbf{Case I}, is also visible in the bivariate marginal plots if we compare the fourth row in Fig. \ref{fig:IEEE14marginalsCase0} with the same in Fig. \ref{fig:IEEE14marginalsCase1}.

@@

To depict the numerical accuracy, Fig. \ref{fig:RelErrSynthetic} plots the (time-varying) relative error between the empirical (i.e., Monte Carlo estimate) mean vector $\bm{\mu}_{k}^{\text{MC}}\in\mathbb{T}^{50}\times\mathbb{R}^{50}$, and the ``proximal mean" vector $\bm{\mu}_{k}^{\text{Prox}}\in\mathbb{T}^{50}\times\mathbb{R}^{50}$. The latter was computed using the proximal updates $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$. Fig. \ref{fig:RelErrSynthetic} shows that the time varying statistics from these two computation match very well at all times.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\linewidth]{IEEE14marginalsCase0.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs of the generator $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup \textbf{Case I} described in Sec. \ref{subsec:NumSimIEEEBus}. The five rows above correspond to the five generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values. The $\theta_i$ are in rad, the $\omega_i$ are in rad/s.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginalsCase0}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\linewidth]{IEEE14marginalsCase1.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs of the generator $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup \textbf{Case II} described in Sec. \ref{subsec:NumSimIEEEBus}. The five rows above correspond to the five generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values. The $\theta_i$ are in rad, the $\omega_i$ are in rad/s.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginalsCase1}
\end{figure*}

@@

Fig. \ref{fig:IEEE14omegamarginalsCase12} shows the corresponding univariate $\omega_{i}$-marginal PDFs. In particular, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) helps compare the $\omega_{4}$ marginal evolution for bus 6 in the nominal (\textbf{Case I}) and post-fault (\textbf{Case II}) scenarios. Since \textbf{Case II} considers the failure of line 13, from Fig. \ref{fig:Motivating} we intuitively expect that the transient effects of this fault will be prominent for bus 6 (generator 4). Indeed, Fig. \ref{fig:IEEE14omegamarginalsCase12}(c) shows that although the $\omega_{4}$ marginals in both \textbf{Case I} and \textbf{II}, at all times have the highest probability around $0$ rad/s, the post-fault marginals show larger spread or dispersion of the probability mass, as expected. That the generator 4 states in \textbf{Case II} have larger uncertainties than in \textbf{Case I}, is also visible in the bivariate marginal plots if we compare the fourth row in Fig. \ref{fig:IEEE14marginalsCase0} with the same in Fig. \ref{fig:IEEE14marginalsCase1}.

@@

To depict the numerical accuracy, Fig. \ref{fig:RelErrSynthetic} plots the (time-varying) relative error between the empirical (i.e., Monte Carlo estimate) mean vector $\bm{\mu}_{k}^{\text{MC}}\in\mathbb{T}^{50}\times\mathbb{R}^{50}$, and the ``proximal mean" vector $\bm{\mu}_{k}^{\text{Prox}}\in\mathbb{T}^{50}\times\mathbb{R}^{50}$. The latter was computed using the proximal updates $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$. Fig. \ref{fig:RelErrSynthetic} shows that the time-varying statistics from these two computation match very well at all times.
